---
title: "RWorksheet_Canonicato#6"
author: "Dianah Marie Canonicato"
date: "2023-12-06"
output:
  pdf_document: default
  html_document: default
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#1
```{r}

test <- data.frame(Student = c(1,2,3,4,5,6,7,8,9,10),
                   PreTest = c(55,54,47,57,51,61,57,54,63,58),
                   PostTest =c(61,60,56,63,56,63,59,56,62,61))
test

#a.Compute the descriptive statistics using different packages (Hmisc and pastecs).

library(Hmisc)
library(pastecs)

summary_hmisc <- describe(test[,c("PreTest","PostTest")])
summary_hmisc


summary_pastecs <- stat.desc(test)
summary_pastecs



```
#2
```{r}

library(dplyr)

Fertelizer_Level <- c(10, 10, 10, 20, 20, 50, 10, 20, 10, 50, 20, 50, 20, 10)
OrderedFertilizer <- factor(Fertelizer_Level, levels =unique(Fertelizer_Level))

basicStats <- summary(OrderedFertilizer)
basicStats

#The result is the ordered version of the original data, with the values arranged in ascending order.


```
#3
```{r}
excercise_Levels <- c("n", "l", "n", "n", "l", "l", "n", "n", "i", "l")

ExerciseFactor <- factor(excercise_Levels, levels = c("n","l","i"))


basic_stats <- summary(ExerciseFactor)
basic_stats
```
#4
```{r}
#Using a factor variable is the most effective method for expressing the workout levels in R.
#The three choices for activity levels in this instance are "n" (none), "l" (light), and "i" (intense). 
#To appropriately describe the activity levels for each participant, you can use these levels to generate a factor variable.

state <- c("tas", "sa", "qld", "nsw", "nsw", "nt", "wa", "wa", "qld","vic", "nsw", "vic", "qld", "qld", "sa", "tas", "sa", "nt",
"wa", "vic", "qld", "nsw", "nsw", "wa", "sa", "act", "nsw",
"vic", "vic", "act")

state_Factor <- factor(state)
state_Factor

summary_State <- summary(state_Factor)
summary_State

#The result will show the original state data, the factor levels, and the factor representation. 
#The factor levels will be automatically assigned based on the unique values in the state vector.
```
#5
```{r}
incomes <- c(60, 49, 40, 61, 64, 60, 59, 54,
             62, 69, 70, 42, 56, 61, 61, 61, 58, 51, 48,
             65, 49, 49, 41, 48, 52, 46, 59, 46, 58, 43)

IncomeMean <- tapply(incomes, state_Factor, mean)
IncomeMean

```
#5b
```{r}

# act      nsw       nt      qld     sa      tas      vic       wa 
#44.50000 57.33333 55.50000 53.60000 55.00000 60.50000 56.00000 52.25000 

#These results suggest that there are differences in income levels among the states. Further analysis and comparison of these mean income values can provide insights into the economic disparities and potential factors influencing income distribution across different regions.
```
#6
#a
```{r}
#a. What is the standard error? Write the codes.

std_Error <- function(x) sqrt(var(x)/length(x))
incster <- tapply(incomes, state, std_Error)
standard_Error <- tapply(incomes, state_Factor, std_Error)
standard_Error

```
#6b
```{r}
#The resulting output provides the standard error values for each state or state factor. The states or state factors are listed as the row names, and the corresponding standard error values are displayed in the adjacent column.

#the standard error values provide insights into the variability of incomes across different states or state factors. States with higher standard error values indicate greater variability in incomes, while states with lower standard error values suggest more consistent incomes
```
#7
#a
```{r}
library(titanic)

data("titanic_train")
titanic_data <- titanic_train

str(titanic_data)

subs_Survived <- subset(titanic_data, Survived == 1)


subs_Dead <- subset(titanic_data, Survived == 0)
subs_Dead

head(subs_Survived)
head(subs_Dead)
```
#8 chronologihttps://drive.google.com/file/d/16MFLoehCgx2MJuNSAuB2CsBy6eDIIr-u/view?usp=drive_link)

a. describe what is the dataset all about.
```{r}
##The dataset consists of cytological features of breast cancer cell samples, such as clump thickness, size uniformity, shape uniformity, marginal adhesion, epithelial size, bare nucleoli, bland chromatin, normal nucleoli, mitoses, and the corresponding class labels, with various records containing information on benign or malignant tumors.
```


```{r}
library(readr)
library(rcompanion)
breastcancer_wisconsin <- read_csv("breastcancer_wisconsin (1).csv",col_types = cols(
  id = col_double(),
  clump_thickness = col_double(),
  size_uniformity = col_double(),
  shape_uniformity = col_double(),
  marginal_adhesion = col_double(),
  epithelial_size = col_double(),
  bare_nucleoli = col_character(),
  bland_chromatin = col_double(),
  normal_nucleoli = col_double(),
  mitoses = col_double(),
  class = col_double()
))
breastcancer_wisconsin

```
#d.1 Standard error of the mean for clump thickness.

```{r}

clump_thickness <- sd(breastcancer_wisconsin$clump_thickness) / sqrt(length(breastcancer_wisconsin$clump_thickness))
cat("d.1 Standard Error of the Mean for Clump Thickness:", clump_thickness, "\n")
```
# d.2 Coefficient of variability for Marginal Adhesio

```{r}
marginal_adhesion <- sd(breastcancer_wisconsin$marginal_adhesion) / mean(breastcancer_wisconsin$marginal_adhesion) * 100
cat("d.2 Coefficient of Variability for Marginal Adhesion:", marginal_adhesion, "%\n")
```
# d.3 Number of null values of Bare Nuclei.
```{r}
values_bare_nuclei <- sum(is.na(breastcancer_wisconsin$bare_nucleoli))
cat("d.3 Number of Null Values in Bare Nuclei:", values_bare_nuclei, "\n")

```
# d.4 Mean and standard deviation for Bland Chromatin.
```{r}
mean_bland_chromatin <- mean(breastcancer_wisconsin$bland_chromatin)
mean_bland_chromatin
sd_bland_chromatin <- sd(breastcancer_wisconsin$bland_chromatin)
cat("d.4 Mean for Bland Chromatin:", mean_bland_chromatin, "\n")
cat("   Standard Deviation for Bland Chromatin:", sd_bland_chromatin, "\n")

```
# d.5 Confidence interval of the mean for Uniformity of Cell Shape.
```{r}
uniformity_of_cell_shape <- t.test(breastcancer_wisconsin$shape_uniformity, conf.level = 0.95)$conf.int
cat("d.5 Confidence Interval for the Mean of Uniformity of Cell Shape:", uniformity_of_cell_shape, "\n")

```
#d. How many attributes?
```{r}
#There are 11 attributes in the data set.
```
#e. Find the percentage of respondents who are malignant. Interpret the results
```{r}
#assuming class 4 is malignant
percentage_malignant <- (sum(breastcancer_wisconsin$class == 4)/ nrow(breastcancer_wisconsin)) * 100
cat("The percentage of respondents who are malignant are: ",percentage_malignant,"%")
```
#9.
```{r}
#install.packages("AppliedPredictiveModeling")
library("AppliedPredictiveModeling")

data("abalone")
head(abalone)
summary(abalone)

#export
#install.packages("xlsxjars")
library(xlsx)
write.xlsx(abalone, "Abalone.xlsx")
```